---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# ggbezier

<!-- badges: start -->
<!-- badges: end -->

`ggbezier` makes it easy to work with [Bezier curves](https://en.wikipedia.org/wiki/B%C3%A9zier_curve) in `ggplot2.

## Installation

You can install the development version of ggbezier from Github:

``` r
devtools::install_github("const-ae/ggbezier")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(ggplot2)
library(ggbezier)

# Only recommended, but not required
library(dplyr)
```


Bezier curves are useful for drawing wavy things.

```{r}
wave_data <- data.frame(
  x = seq(1, 12, by = 2),
  y = rep(c(0.5, -0.5), times = 3)
)

ggplot(wave_data, aes(x = x, y = y)) +
    geom_bezier()
```

The shape is controlled by _control points_ of handles. Set `draw_handles = TRUE` to see them.

```{r}
ggplot(wave_data, aes(x = x, y = y)) +
    geom_bezier(show_handles = TRUE)
```

You can change the handles by setting

* their `angle` and `handle_length`, or
* the position of the next end point (`x_handle` and `y_handle`), or
* the position of the left and right handle (`x_handle1`, `y_handle1`, `x_handle2`, and `y_handle2`).

```{r}
ggplot(wave_data, aes(x = x, y = y)) +
    geom_bezier(show_handles = TRUE, angle = 20)
```

Data with randomized handle positions:

```{r}
wave_data %>%
  mutate(x_handle1 = x + rnorm(n(), sd = 0.4),
         x_handle2 = x + rnorm(n(), sd = 0.4),
         y_handle1 = y + rnorm(n(), sd = 0.4),
         y_handle2 = y + rnorm(n(), sd = 0.4)) %>%
  ggplot(aes(x = x, y = y, x_handle1 = x_handle1, x_handle2 = x_handle2, y_handle1 = y_handle1, y_handle2 = y_handle2)) +
    geom_bezier(show_handles = TRUE, show_curve = FALSE, color = "green") +
    geom_bezier(show_handles = FALSE, show_curve = TRUE, color = "black") +
    lims(y = c(-1, 1))
```


Bezier curves are also useful for drawing pretty arrows and annotating datapoints:

```{r}
ggplot(mtcars, aes(x = cyl, y = mpg)) +
    geom_point() +
    geom_bezier(data = data.frame(x = c(6.05, 6.5), y = c(19.7, 15), angle = c(0, -90), handle_length = c(0.4, 5)),
                aes(x = x, y = y, angle = angle, handle_length = handle_length),
                arrow = arrow(type = "closed", ends = "first")) +
    annotate("text", x = 6.5, y = 15, hjust = 0.5, vjust = 1.1, label = "Ferrari Dino")
```



```{r}
sessionInfo()
```


